# Employee Salaries for different job roles

1.  Uploading the data

```{r}
getwd()
```

```{r}
setwd("C:/Users/parul/Desktop/Congno Rise Internship")
```

```{r}
ds_salaries<-read.csv("C:/Users/parul/Desktop/Congno Rise Internship/ds_salaries.csv")
```

```{r}
ds_salaries
```

2.  Downloading the packages required

```{r}
library("ggplot2")
```

```{r}
library("dplyr")
```

```{r}
library("corrplot")
```

```{r}
install.packages("plotly")
```

```{r}
library("plotly")
```

```{r}
library("tidyr")
```

3.  Running the regression to predict salary

```{r}
lm_salary<-lm(salary~X+work_year+experience_level+employment_type+job_title+
                employee_residence+remote_ratio+company_location+company_size,data = ds_salaries)
```

```{r}
summary(lm_salary)
```

3.  Summary Statistics for numerical values

```{r}
summary(ds_salaries[c("salary","salary_in_usd")])
```

4.  ANOVA to test the differences in salary by work_year

```{r}
aov_salary_work_year<-aov(salary~work_year,data=ds_salaries)
```

```{r}
summary(aov_salary_work_year)
```

5.  ANOVA to test the differences in salary by experience_level

```{r}
aov_salary_experience_level<-aov(salary~experience_level,data = ds_salaries)
```

```{r}
summary(aov_salary_experience_level)
```

6.  Correlation between numeric variables

```{r}
cor_matt<-cor(ds_salaries[c("X","salary","salary_in_usd")])
```

```{r}
cor_matt
```

```{r}
corrplot(cor_matt,method = "circle",tl.srt=45,type="upper",tl.cex = 0.5,tl.col = "black")
```

7.  Box plot to visualize salary distribution according to work year

```{r}
ggplot(ds_salaries, aes(x = experience_level, y = salary)) +
  geom_boxplot(fill="purple") +
  theme_minimal() + 
  labs(title = "Salary by Experience Level")
```

8.  Boxplot

```{r}
ggplot(ds_salaries, aes(x = experience_level, y = salary)) + 
  geom_boxplot() +
  facet_wrap(~work_year) +
  theme_minimal() + 
  labs(title = "Salary by Experience Level and Work Year")
```

9.  Box plot of salary by Job Title

```{r}
ggplot(ds_salaries, aes(x = job_title, y = salary)) + 
  geom_boxplot(fill="thistle",color="#35063E") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  labs(title = "Boxplot of Salary by Job Title",x="Job Title",y="Salary")
```

10. Histogram of Salary

```{r}
ggplot(ds_salaries,aes(x=salary))+
  geom_histogram(bins = 30,fill="#9F87E3")+
  theme_minimal()+
  labs(title = "Histogram of Salary",x="Salary",y="Frequency")
```

11. Bar plot of job title frequencies

```{r}
ggplot(ds_salaries, aes(x = job_title)) + 
  geom_bar(fill="#C25283") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  labs(title = "Bar Plot of Job Title Frequencies",x="Job Title",y="Count")
```

12. Bar plot of employee residence frequencies

```{r}
ggplot(ds_salaries, aes(x = employee_residence)) + 
  geom_bar(fill="#4E1F33") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  labs(title = "Bar Plot of Employee Residence Frequencies",x="Employee Residence",y="Count")
```

13. Histogram of Salary by work year

```{r}
ggplot(ds_salaries, aes(x = salary)) + 
  geom_histogram(bins = 30,fill="navy") + 
  facet_wrap(~work_year) + 
  labs(title = "Histogram of Salary by Work Year")
```

14. Donut Chart for Employment Type

```{r}
employment_type_counts <- table(ds_salaries$employment_type)
```

```{r}
employment_type_counts
```

```{r}
plot_ly(ds_salaries,labels= ~employment_type,type = "pie",hole=0.7,textposition="inside")
```

15. Donut Chart for Company size

```{r}
plot_ly(ds_salaries,labels= ~company_size,type="pie",hole=0.5,textposition="inside")
```

16. Number of Companies as per Remote ratio

```{r}
ggplot(ds_salaries,aes(x=remote_ratio))+
  geom_bar(fill="#CCCAA8")+
  labs(title="Number of Companies as per Remote Ratio",x="Remote Ratio",y="Count")+
  theme_minimal()
```

17. Number of Companies as per Company's Location

```{r}
ggplot(ds_salaries,aes(x=company_location))+
  geom_bar(fill="#496679")+
  labs(title = "Number of Companies as per Location",x="Company's Location",y="Count")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
